\documentclass[a4paper]{article}

\usepackage{a4wide,times}
\usepackage[english]{babel}
\usepackage{listings}

\lstset{
language=c,
basicstyle=\ttfamily,
numbers=left,
numberstyle=\footnotesize,
stepnumber=1,
numbersep=5pt,
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=t,
breaklines=true,
breakatwhitespace=false,
}

\begin{document}


\title{Code Conventions}
\author{Thomas Versteeg \quad Job Talle}

\maketitle

\section{Conventions}
\subsection{Example Code}
\emph{Header:}
\begin{lstlisting}
    #pragma once
     
    #include <stdlib.h>
    #include "dingen.h"
     
    /* Does random shit */
    int function(char *destination, const char *source, int value);
\end{lstlisting}
\emph{Body:}
\begin{lstlisting}
    #include "header.h"
     
    typedef struct{
        int variable;
        char *string;
    } Struct;
     
    typedef struct _StructStruct{
        struct _StructStruct *next;
    } StructStruct;
     
    typedef enum{
        A = 1,
        BETA = 2
    } Enum;
     
    int function(char *destination, const char *source, int value)
    {
        int i, j, output;
        /* Random loop */
        for(i = 0; i < strlen(source); i++){
            for(j = 0; j < value; j++){
                destination[i] += j;
            }
        }  
        return output;
    }


\end{lstlisting}

\subsection{Naming}
CamelCase is applied for naming all variables and structures. All variables and functions should start with a lowercase letter. Some exceptions exist.

\emph{Structures} and \emph{enumerations} are the only entities starting with an uppercase letter.

Locally used structures and variables can start with an underscore to avoid naming conflicts, or to clarify their local nature.

\subsection{spaces}
Spaces are used around operators, as seen in the example code. They are not used before the \emph{\{}.

\subsection{OOP}
Structs are initialized with a function named newStruct (where Struct is the structure name), and freed using freeStruct. Function pointers are assigned in the newStruct function.

\end{document}